Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-04-06 aosd13/paperBody.tex
Revisions from Klaus on AOSD13 text

After describing how to use {\LoS}, we explain how \LoS{} represents queries internally and optimizes them.
\begin{techrep}
Here we give only a brief overview of our implementation technique; it is described in more detail
in Appendix~\ref{sec:intfScala}.
\end{techrep}
\begin{nontechrep}
We give only a brief overview of our implementation technique; it is described in more detail
in a technical report that accompanies this paper~\citep{GiarrussoEtAl2012ReifyTR}.
\end{nontechrep}

@@

\chapter{Collection query embedding as a case study}
\label{sec:caseStudy}
In this chapter we discuss collections as a \emph{critical} case
study~\citep{flyvbjerg06five} for deep DSL embedding.

>>>>

After describing how to use {\LoS}, we explain how \LoS{} represents queries internally and optimizes them.
\begin{techrep}
Here we give only a brief overview of our implementation technique; it is described in more detail
in \cref{sec:intfScala}.
\end{techrep}
\begin{nontechrep}
We give only a brief overview of our implementation technique; it is described in more detail
in a technical report that accompanies this paper~\citep{GiarrussoEtAl2012ReifyTR}.
\end{nontechrep}

@@

\chapter{A deep EDSL for collection queries}
\label{sec:caseStudy}
In this chapter we discuss collections as a \emph{critical} case
study~\citep{flyvbjerg06five} for deep DSL embedding.
